On g~0~

### 2017-03-21 manuscript.Rmd
Hakea figure updated

\
Remko A. Duursma^1^, Chris Blackman^1^, Belinda Medlyn^1^

@@

```{r echo=FALSE}
includefigs <- TRUE
library(png)
library(grid)

plotfig <- function(...)grid.raster(readPNG(...))
```

@@

Importance of stomatal conductance. Prevalence of the Ball-Berry model, and g0. What is g0? Point of this paper.

@@

```{r, echo=FALSE, eval=FALSE}
with(subset(kerst, method == "gcut_isol"), summary(gmin))
with(subset(rieder, gmin < 100000), summary(gmin))
```

@@

Minimum conductance from Blackman (WTC4). See Drake for WTC4 methods.

@@

[@medlyn_reconciling_2011] does not develop theory for g0, instead adds it as a minimum conductancce because that's how it is!

@@

@@

# Components of g0

@@

@@

## Cuticular

@@

## nighttime
Nighttime conductance not necessarily same as minimum conductance
We are not reviewing nighttime conductance here, that has been done extensively by others [@caird2007]

@@

## minimum conductance

@@

@@

**Figure 4**. Comparison of various estimates of minimum conductance. Error bars are standard errors, grey vertical lines 90% quantiles indicating wide range of variation for any variable. g~cut,isol~ : cuticual permeance measured on isolated cuticles that lack stomata (data from Kerstiens 1996), g~min,seal~ : minimum conductance based on leaf dry-down curves where the side of the leaf that bears stomata is sealed (data from Kerstiens 1996), g~min~ : minimum conductance based on leaf-dry-down curves (data from Kerstiens 1996, and more added), g~dark : stomatal conductance at night, measured in field conditions (data from Lombardozzi et al. 2017), g~0~ fitted g~0~ in the Medlyn et al. (2011) model with the Lin et al. (2015) database, g~s,low A~ : for the Lin et al. (2015) database, minimum g~s~ when net assimilation rate was less than 2 $mu$ mol m^-2^ s^-1^, calculated once for each dataset.

@@

**Figure 5**. Analysis of g~min~ from Figure 4 by plant growth form and phylogenetic group. Different letters denote significant differences at $alpha$ = 0.05. The groups Trees are split by angiosperms and gymnosperms.

@@

**Figure 6**.

>>>>

\
Remko A. Duursma^1^, Chris Blackman^1^, Rosana Lopéz^1^, Belinda Medlyn^1^

@@

```{r echo=FALSE}
includefigs <- FALSE
library(png)
library(grid)

plotfig <- function(...)grid.raster(readPNG(...))

source("R/load.R")

pval <- function(...)formatPval(..., includeEquality=TRUE)
```

@@

Importance of stomatal conductance. Prevalence of the Ball-Berry model. Parameters are g1 and g0. 
What is g0? Point of this paper.

We argue that

- we need g0 to get responses at low light correct, and probably at high T
- g0 is poorly estimated as the intercept, with the usual regression technique
- can we estimate g0 independently? Some assume that g0 = gdark but that's rubbish. It is also much larger than cuticular conductance, but seems roughly consistent with gmin (minimum conductance from leaf dry-down curves).
- there is inter-specific variation in gmin that is related to growth form 
- gmin is a plastic trait as it responds to growth at elevated temperature, and growth in dry soil
- models should consider night-time conductance and daily minimum conductance as distinctly separate processes.

@@

@@

Minimum conductance from Blackman (WTC4). See Drake for WTC4 methods.
gmin Hakea, same methods (measurement T?)

@@

[@medlyn_reconciling_2011] does not develop theory for g0, instead adds it as a minimum conductance because that's how it is!

@@

 **Cite Figure 1**

@@

**Cite Figure 2 and 3**

# Definitions of minimum conductance

@@

**Cite Figure 4**

@@

## Cuticular permeance

@@

## Night-time conductance

Nighttime conductance not necessarily same as minimum conductance
We are not reviewing nighttime conductance here, that has been done extensively by others [@caird2007]

@@

## Minimum conductance from leaf-dry down curves

@@

** cite figures 5,6 and 7**

@@

**Figure 4**. Comparison of various estimates of minimum conductance. Error bars are standard errors, grey vertical lines 90% quantiles indicating wide range of variation for any variable. g~cut,isol~ : cuticual permeance measured on isolated cuticles that lack stomata (data from Kerstiens 1996), g~min,seal~ : minimum conductance based on leaf dry-down curves where the side of the leaf that bears stomata is sealed (data from Kerstiens 1996), g~min~ : minimum conductance based on leaf-dry-down curves (data from Kerstiens 1996, with a few extra data points - to be added), g~dark : stomatal conductance in the dark at night, measured in field conditions (data from Lombardozzi et al. 2017), g~0~ : fitted g~0~ in the Medlyn et al. (2011) model with the Lin et al. (2015) database, g~s,low A~ : for the Lin et al. (2015) database, minimum g~s~ when net assimilation rate was less than 2 $mu$ mol m^-2^ s^-1^, calculated once for each dataset.

@@

**Figure 5**. Analysis of g~min~ from Figure 4 by plant growth form and phylogenetic group. Different letters denote significant differences at $alpha$ = 0.05. The groups 'Angiosperm' and 'Gymnosperm' include trees only.

@@

**Figure 6**. Minimum conductance measured from leaf dry-down curves on *Eucalyptus parramattensis* grown in whole-tree chambers. Trees were grown following ambient conditions, or in a constant elevated temperature treatment (+3 degrees C). Measurements of g~min~ were carried out at five different temperatures on replicate leaves. There is no effect of measurement T on g~min~, but leaves of trees grown in elevated temperature showed consistently lower g~min~.

```{r fig.height=4,echo=FALSE, eval=includefigs}
plotfig("output/figure7.png")
```

**Figure 7**. Minimum conductance measured from leaf dry-down curves on a variety *Hakea* species, a genus native to Australia. Plants were grown in containers in a grow house, and supplied with ample water or underwent long-term mild drought stress. Bars are labelled by leaf form : broadleaf (B) or needle-like (N). g~min~ was higher for species with needle-like leaves, both for well-watered plants (Wilcoxon test, p `r pval(wilcox.test(gmin.w ~ leaf.form, data=lopw)$p.value)`) and droughted plants (p `r pval(wilcox.test(gmin.d ~ leaf.form, data=lopw)$p.value)`).
